Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-07-11 doc/RMD/mlg-mcg.Rmd
add counts of MLG/MCG pairs

>>>>

Of interest is accounting for the communities that have a single MCG/MLG pair.
We can detect these by filtering for communities that only have two members:

```{r}
singles <- the_communities %>% 
  count(community) %>% 
  arrange(desc(n)) %>% 
  filter(n == 2) %>% 
  inner_join(the_communities, by = "community") %>% 
  mutate(type = case_when(grepl("MLG", vertex) ~ "MLG", TRUE ~ "MCG")) %>% 
  spread(type, vertex) %>%
  select(-n, -comm)
# assessing that this truely contains the singletons
nrow(inner_join(singles, the_communities, by = c("MCG" = "vertex")))
nrow(inner_join(singles, the_communities, by = c("MLG" = "vertex")))

knitr::kable(singles)
```
